BERT Model Compression and Weight Sharing

### 2019-05-12 paper/paper.tex
Write DeepTwist discussion section

Things to say about DeepTwist
\begin{itemize}
  \item Stratified prune better
  \item Prune rate mad robust
  \item Diff gud
  \item ``Improved performance''
  \item QQP takes long, but looks okay
  \item Didn't try only pruning the $\bert$ part
\end{itemize}

Things to say about KD
\begin{itemize}
  \item it bad
  \item doesn't work
  \item LSTM weird/CNN incredibly noisy
  \item \TODO{compare}
\end{itemize}

@@

\begin{itemize}
\item What conclusions can you draw from the results section?
\item Is there further analysis you can do into the results of the system? Here
is a good place to include visualizations, graphs, qualitative analysis of your
results.

\item  What questions remain open? What did you think might work, but did not?
\end{itemize}

>>>>

Our most striking result is the robust performance of difference pruning. Even
keeping upwards of 99\% of the weights unchanged gives us performance that is
very competitive with the unrestricted model. Most of our experiments are on
SST-2, but we see success with this method on QQP as well, suggesting that
small changes to pre-trained BERT are sufficient for performance on a specific
task.

As expected, pruning a higher proportion of the weights decreases performance,
but we are happily surprised at the relatively low magnitude of this effect even
at high prune rates. Pruning with a global threshold rather than in a
stratified way produces distinctly worse results. We suspect this is due to
weights in different layers having different magnitudes, making a global
threshold have an undue effect on layers whose weights tend to be smaller. We
confirm this heterogeneity in 
% TODO: include box-plots of weights

Our non-difference distortions are more sensitive to the compression parameter
(whether prune rate or SVD rank). We find it difficult to achieve performance
comparable to the uncompressed BERT with a significantly compressed model. Among
the different distortion methods, we favor pruning for its computational
simplicity, and see no evidence that SVD achieves better compression.

% Things to say about DeepTwist
% \begin{itemize}
%   \item Stratified prune better
%   \item Prune rate mad robust
%   \item Diff gud
%   \item ``Improved performance''
%   \item QQP takes long, but looks okay
%   \item Didn't try only pruning the $\bert$ part
% \end{itemize}
% 
% Things to say about KD
% \begin{itemize}
%   \item it bad
%   \item doesn't work
%   \item LSTM weird/CNN incredibly noisy
%   \item \TODO{compare}
% \end{itemize}

@@

% \begin{itemize}
% \item What conclusions can you draw from the results section?
% \item Is there further analysis you can do into the results of the system? Here
% is a good place to include visualizations, graphs, qualitative analysis of your
% results.
% 
% \item  What questions remain open? What did you think might work, but did not?
% \end{itemize}
